Tropical Andes plant Lookup Table

### 2023-12-06 code/L1/L1_P2_TropicalAndes_taxcleaning.Rmd
update NA removal code so it works, filter trait data to species in lookup table, export filtered data

# Disparties
all_species_no.opinion <- subset(all_species_hamonized_results, Taxonomic_status == "No opinion")
nrow(all_species_no.opinion)
all_species_illegitimate <- subset(all_species_hamonized_results, Taxonomic_status == "Illegitimate")
nrow(all_species_illegitimate)
all_species_invalid <- subset(all_species_hamonized_results, Taxonomic_status == "Invalid")
nrow(all_species_invalid)
all_species_other <- subset(all_species_hamonized_results, Taxonomic_status == "")
nrow(all_species_other)
all_species_NA <- subset(all_species_hamonized_results, Taxonomic_status == NA)
nrow(all_species_NA)
```
# Create species list of names with disparities
```{r}
all_species_disparities <- all_species_hamonized_results %>%
                            filter(Taxonomic_status %in% c("No opinion", "Illegitimate", "Invalid", "")) %>%
                            select(Name_submitted)
nrow(all_species_disparities)
```

@@

# Save lookup table as csv
```{r}
write.csv(lookup_table, file.path(output_path,"plant_lookup_table.csv"), row.names = FALSE)
```

@@

## BIEN
```{r}

```

## GIFT
```{r}

```

# Summary
```{r}
source("~/GitHub/neotropical_plants/functions/data_summary.R")
```

```{r}
data_summary(GBIF_occ_subset_harmonized, GBIF_occ_subset_harmonized$species, GBIF_occ_subset_harmonized$genus, GBIF_occ_subset_harmonized$family)
```

# Write data to csv
```{r}

```

>>>>

# Disparties
all_species_no.opinion <- subset(all_species_hamonized_results, Taxonomic_status == "No opinion")
nrow(all_species_no.opinion)
all_species_illegitimate <- subset(all_species_hamonized_results, Taxonomic_status == "Illegitimate")
nrow(all_species_illegitimate)
all_species_invalid <- subset(all_species_hamonized_results, Taxonomic_status == "Invalid")
nrow(all_species_invalid)
all_species_other <- subset(all_species_hamonized_results, Taxonomic_status == "")
nrow(all_species_other)
all_species_NA <- subset(all_species_hamonized_results, is.na(all_species_hamonized_results$Taxonomic_status))
nrow(all_species_NA)
```
# Create species list of names with disparities
```{r}
all_species_disparities <- all_species_hamonized_results %>%
                            filter(Taxonomic_status %in% c("No opinion", "Illegitimate", "Invalid", "", NA)) %>%
                            select(Name_submitted)
nrow(all_species_disparities)
```

@@

# Save lookup table and unresolved species list as csv
```{r}
write.csv(lookup_table, file.path(output_path,"plant_lookup_table.csv"), row.names = FALSE)
write.csv(unresolved_species, file.path(output_path,"plant_unresolved_species.csv"), row.names = FALSE)
```

@@

## BIEN
```{r}
# filter data to species in lookup_table$Names_submitted
BIEN_traits_subset <- BIEN_traits %>%
  filter(scrubbed_species_binomial %in% lookup_table$Name_submitted)
nrow(BIEN_traits_subset)
# filter lookup_table to species in data
lookup_table_subset <- lookup_table %>%
  filter(Name_submitted %in% BIEN_traits_subset$scrubbed_species_binomial)
nrow(lookup_table_subset)

## add accepted species column from lookup table based on species column
BIEN_traits_subset_harmonized <- right_join(lookup_table_subset, BIEN_traits_subset, join_by(Name_submitted == scrubbed_species_binomial), keep = TRUE, relationship = "one-to-many")
nrow(BIEN_traits_subset_harmonized)
```

## GIFT
```{r}
GIFT_traits_subset <- GIFT_traits %>%
  filter(species %in% lookup_table$Name_submitted)
nrow(GIFT_traits_subset)
# filter lookup_table to species in data
lookup_table_subset <- lookup_table %>%
  filter(Name_submitted %in% GIFT_traits_subset$species)
nrow(lookup_table_subset)

## add accepted species column from lookup table based on species column
GIFT_traits_subset_harmonized <- right_join(lookup_table_subset, GIFT_traits_subset, join_by(Name_submitted == species), keep = TRUE, relationship = "one-to-many")
nrow(GIFT_traits_subset_harmonized)
```

# Summary
## GBIF
```{r}
print("Number of records: ")
nrow(GBIF_occ_subset_harmonized)
print("Number of species: ")
length(unique(GBIF_occ_subset_harmonized$Accepted_species))
```

## TRY
```{r}
print("Number of records: ")
nrow(TRY_traits_subset_harmonized)
print("Number of species: ")
length(unique(TRY_traits_subset_harmonized$Accepted_species))
```

## BIEN
```{r}
print("Number of records: ")
nrow(BIEN_traits_subset_harmonized)
print("Number of species: ")
length(unique(BIEN_traits_subset_harmonized$Accepted_species))
```

## GIFT
```{r}
print("Number of records: ")
nrow(GIFT_traits_subset_harmonized)
print("Number of species: ")
length(unique(GIFT_traits_subset_harmonized$Accepted_species))
```

# Write data to csv
```{r}
write.csv(GBIF_occ_subset_harmonized, file.path(output_path,"TropicalAndes_GBIF_plant_occ_harmonized.csv"), row.names = FALSE)
write.csv(TRY_traits_subset_harmonized, file.path(output_path,"TropicalAndes_TRY_plant_traits_harmonized.csv"), row.names = FALSE)
write.csv(BIEN_traits_subset_harmonized, file.path(output_path,"TropicalAndes_BIEN_plant_traits_harmonized.csv"), row.names = FALSE)
write.csv(GIFT_traits_subset_harmonized, file.path(output_path,"TropicalAndes_GIFT_plant_traits_harmonized.csv"), row.names = FALSE)
```
